---
title: "Multi-Species Occupancy-Detection Model Master File"
author: "Annalie Dorph"
date: "September 22nd 2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

Load libraries
```{r libraries}
require(rjags)
require(jagsUI)
require(tidyverse)
require(ggplot2)
require(cowplot)
require(grid)
require(gridExtra)
require(data.table)
```

Load functions for data preparation and summaries of output
```{r functions}
#Data preparation
source("./code/data_preparation.R")
source("./code/summary_functions.R")
```

Create subdirectories to save your data
```{r repositories}
ifelse(dir.exists("./jagsoutput/"), TRUE, dir.create("./jagoutput/"))
ifelse(dir.exists("./species_prediction/"), TRUE, dir.create("./species_prediction/"))
```

Regression coefficients used included:

* Temperature
* Temperature (quadratic)
* Date
* Date (quadratic)

**Model 1** will test broad priors for the regression coefficients
Prior specification
mu hyperdistributions: wide normal priors (sd of 31 ie precision 0.001)
sd hyperdistributions: uniform priors [0-10]
```{r model1}
# Define model in BUGS language
sink("MSODM_jags_v1.txt")
cat("
    model {

    # Priors
    # Hyperparameters
    for(k in 1:nspec){                                  # Loop over all species in array
      lpsi[k] ~ dnorm(mu.lpsi, tau.lpsi)                # Baseline community occupancy probability
      lp[k] ~ dnorm(mu.lp, tau.lp)                      # Baseline community detection probability
      # Covariate effects on detection:
      betalp1[k] ~ dnorm(mu.betalp1, tau.betalp1)
      betalp2[k] ~ dnorm(mu.betalp2, tau.betalp2)
      betalp3[k] ~ dnorm(mu.betalp3, tau.betalp3)
      betalp4[k] ~ dnorm(mu.betalp4, tau.betalp4)
    }

    # Hyperpriors for community hyperparameters in occupancy
    mu.lpsi ~ dnorm(0,0.001)                            # Community means of occupancy probability
    tau.lpsi <- pow(sd.lpsi, -2)                        # Community precision of occupancy probability
    sd.lpsi ~ dunif(0,10)                                # Community dispersion

    # Hyperpriors for community hyperparameters in detection
    mu.lp ~ dnorm(0,0.001)                              # Community means of detection probability
    tau.lp <- pow(sd.lp, -2)                            # Community precision of detection probability
    sd.lp ~ dunif(0,10)                                 # Community dispersion

    mu.betalp1 ~ dnorm(0,0.001)
    tau.betalp1 <- pow(sd.betalp1, -2)
    sd.betalp1 ~ dunif(0,10)
    mu.betalp2 ~ dnorm(0,0.001)
    tau.betalp2 <- pow(sd.betalp2, -2)
    sd.betalp2 ~ dunif(0,10)
    mu.betalp3 ~ dnorm(0,0.001)
    tau.betalp3 <- pow(sd.betalp3, -2)
    sd.betalp3 ~ dunif(0,10)
    mu.betalp4 ~ dnorm(0,0.001)
    tau.betalp4 <- pow(sd.betalp4, -2)
    sd.betalp4 ~ dunif(0,10)

    # Ecological model for true occurrence (process model)
    for(k in 1:nspec){                                  # Loop over species
      for (i in 1:nsite) {                              # Loop over sites
        logit(psi[i,k]) <- lpsi[k]
        z[i,k] ~ dbern(psi[i,k])
      }
    }

    # Observation model for replicated detection/nondetection observations
    for(k in 1:nspec){                                  # Loop over species
      for (i in 1:nsite){                               # Loop over sites
        for(j in 1:nrep){                               # Loop over survey
          logit(p[i,j,k]) <- lp[k] +
                             betalp1[k] * temp[i,j] + betalp2[k] * pow(temp[i,j], 2) +
                             betalp3[k] * date[i,j] + betalp4[k] * pow(date[i,j], 2)
          mu.p[i,j,k] <- z[i,k] * p[i,j,k]
          y[i,j,k] ~ dbern(mu.p[i,j,k])

        }
      }
    }

    # Derived quantities
    for(k in 1:nspec){                                  # Loop over species
      Nocc.fs[k] <- sum(z[,k])                          # Number of occupied sites
    }
    for (i in 1:nsite){                                 # Loop over sites
      Nsite[i] <- sum(z[i,])                            # Number of occurring species at each site
    }

}",fill = TRUE)
sink()
```

**Model 2** will test narrower priors for the regression coefficients
Prior specification
mu hyperdistributions: narrower normal priors (sd of 2.25 ie precision 0.2)
sd hyperdistributions: uniform priors [0-10]
```{r model2}
# Define model in BUGS language
sink("MSODM_jags_v2.txt")
cat("
    model {

    # Priors
    # Hyperparameters
    for(k in 1:nspec){                                  # Loop over all species in array
      lpsi[k] ~ dnorm(mu.lpsi, tau.lpsi)                # Baseline community occupancy probability
      lp[k] ~ dnorm(mu.lp, tau.lp)                      # Baseline community detection probability
      # Covariate effects on detection:
      betalp1[k] ~ dnorm(mu.betalp1, tau.betalp1)
      betalp2[k] ~ dnorm(mu.betalp2, tau.betalp2)
      betalp3[k] ~ dnorm(mu.betalp3, tau.betalp3)
      betalp4[k] ~ dnorm(mu.betalp4, tau.betalp4)
    }

    # Hyperpriors for community hyperparameters in occupancy
    mu.lpsi ~ dnorm(0,0.2)                            # Community means of occupancy probability
    tau.lpsi <- pow(sd.lpsi, -2)                        # Community precision of occupancy probability
    sd.lpsi ~ dunif(0,10)                                # Community dispersion

    # Hyperpriors for community hyperparameters in detection
    mu.lp ~ dnorm(0,0.2)                              # Community means of detection probability
    tau.lp <- pow(sd.lp, -2)                            # Community precision of detection probability
    sd.lp ~ dunif(0,10)                                 # Community dispersion

    mu.betalp1 ~ dnorm(0,0.2)
    tau.betalp1 <- pow(sd.betalp1, -2)
    sd.betalp1 ~ dunif(0,10)
    mu.betalp2 ~ dnorm(0,0.2)
    tau.betalp2 <- pow(sd.betalp2, -2)
    sd.betalp2 ~ dunif(0,10)
    mu.betalp3 ~ dnorm(0,0.2)
    tau.betalp3 <- pow(sd.betalp3, -2)
    sd.betalp3 ~ dunif(0,10)
    mu.betalp4 ~ dnorm(0,0.2)
    tau.betalp4 <- pow(sd.betalp4, -2)
    sd.betalp4 ~ dunif(0,10)

    # Ecological model for true occurrence (process model)
    for(k in 1:nspec){                                  # Loop over species
      for (i in 1:nsite) {                              # Loop over sites
        logit(psi[i,k]) <- lpsi[k]
        z[i,k] ~ dbern(psi[i,k])
      }
    }

    # Observation model for replicated detection/nondetection observations
    for(k in 1:nspec){                                  # Loop over species
      for (i in 1:nsite){                               # Loop over sites
        for(j in 1:nrep){                               # Loop over survey
          logit(p[i,j,k]) <- lp[k] +
                             betalp1[k] * temp[i,j] + betalp2[k] * pow(temp[i,j], 2) +
                             betalp3[k] * date[i,j] + betalp4[k] * pow(date[i,j], 2)
          mu.p[i,j,k] <- z[i,k] * p[i,j,k]
          y[i,j,k] ~ dbern(mu.p[i,j,k])

        }
      }
    }

    # Derived quantities
    for(k in 1:nspec){                                  # Loop over species
      Nocc.fs[k] <- sum(z[,k])                          # Number of occupied sites
    }
    for (i in 1:nsite){                                 # Loop over sites
      Nsite[i] <- sum(z[i,])                            # Number of occurring species at each site
    }
}",fill = TRUE)
sink()
```

**Model 3** will test narrower priors for the regression coefficients
Prior specification
mu hyperdistributions: narrower normal priors (sd of 2.25 ie precision 0.2)
sd hyperdistributions: narrow uniform priors [0-5]
```{r model3}
# # Define model in BUGS language
# sink("MSODM_jags_v3.txt")
# cat("
#     model {
#
#     # Priors
#     # Hyperparameters
#     for(k in 1:nspec){                                  # Loop over all species in array
#       lpsi[k] ~ dnorm(mu.lpsi, tau.lpsi)                # Baseline community occupancy probability
#       lp[k] ~ dnorm(mu.lp, tau.lp)                      # Baseline community detection probability
#       # Covariate effects on detection:
#       betalp1[k] ~ dnorm(mu.betalp1, tau.betalp1)
#       betalp2[k] ~ dnorm(mu.betalp2, tau.betalp2)
#       betalp3[k] ~ dnorm(mu.betalp3, tau.betalp3)
#       betalp4[k] ~ dnorm(mu.betalp4, tau.betalp4)
#     }
#
#     # Hyperpriors for community hyperparameters in occupancy
#     mu.lpsi ~ dnorm(0,0.2)                            # Community means of occupancy probability
#     tau.lpsi <- pow(sd.lpsi, -2)                        # Community precision of occupancy probability
#     sd.lpsi ~ dunif(0,5)                                # Community dispersion
#
#     # Hyperpriors for community hyperparameters in detection
#     mu.lp ~ dnorm(0,0.2)                              # Community means of detection probability
#     tau.lp <- pow(sd.lp, -2)                            # Community precision of detection probability
#     sd.lp ~ dunif(0,5)                                 # Community dispersion
#
#     mu.betalp1 ~ dnorm(0,0.2)
#     tau.betalp1 <- pow(sd.betalp1, -2)
#     sd.betalp1 ~ dunif(0,5)
#     mu.betalp2 ~ dnorm(0,0.2)
#     tau.betalp2 <- pow(sd.betalp2, -2)
#     sd.betalp2 ~ dunif(0,5)
#     mu.betalp3 ~ dnorm(0,0.2)
#     tau.betalp3 <- pow(sd.betalp3, -2)
#     sd.betalp3 ~ dunif(0,5)
#     mu.betalp4 ~ dnorm(0,0.2)
#     tau.betalp4 <- pow(sd.betalp4, -2)
#     sd.betalp4 ~ dunif(0,5)
#
#     # Ecological model for true occurrence (process model)
#     for(k in 1:nspec){                                  # Loop over species
#       for (i in 1:nsite) {                              # Loop over sites
#         logit(psi[i,k]) <- lpsi[k]
#         z[i,k] ~ dbern(psi[i,k])
#       }
#     }
#
#     # Observation model for replicated detection/nondetection observations
#     for(k in 1:nspec){                                  # Loop over species
#       for (i in 1:nsite){                               # Loop over sites
#         for(j in 1:nrep){                               # Loop over survey
#           logit(p[i,j,k]) <- lp[k] +
#                              betalp1[k] * temp[i,j] + betalp2[k] * pow(temp[i,j], 2) +
#                              betalp3[k] * date[i,j] + betalp4[k] * pow(date[i,j], 2)
#           mu.p[i,j,k] <- z[i,k] * p[i,j,k]
#           y[i,j,k] ~ dbern(mu.p[i,j,k])
#
#         }
#       }
#     }
#
#     # Derived quantities
#     for(k in 1:nspec){                                  # Loop over species
#       Nocc.fs[k] <- sum(z[,k])                          # Number of occupied sites
#     }
#     for (i in 1:nsite){                                 # Loop over sites
#       Nsite[i] <- sum(z[i,])                            # Number of occurring species at each site
#     }
# }",fill = TRUE)
# sink()
```

**Model 4** will test mid range priors for the regression coefficients
Prior specification
mu hyperdistributions: narrower normal priors (sd of 2.25 ie precision 0.2)
sd hyperdistributions: narrower uniform priors [2]
```{r model4}
# # Define model in BUGS language
# sink("MSODM_jags_v4.txt")
# cat("
#     model {
#
#     # Priors
#     # Hyperparameters
#     for(k in 1:nspec){                                  # Loop over all species in array
#       lpsi[k] ~ dnorm(mu.lpsi, tau.lpsi)                # Baseline community occupancy probability
#       lp[k] ~ dnorm(mu.lp, tau.lp)                      # Baseline community detection probability
#       # Covariate effects on detection:
#       betalp1[k] ~ dnorm(mu.betalp1, tau.betalp1)
#       betalp2[k] ~ dnorm(mu.betalp2, tau.betalp2)
#       betalp3[k] ~ dnorm(mu.betalp3, tau.betalp3)
#       betalp4[k] ~ dnorm(mu.betalp4, tau.betalp4)
#     }
#
#     # Hyperpriors for community hyperparameters in occupancy
#     mu.lpsi ~ dnorm(0,0.2)                            # Community means of occupancy probability
#     tau.lpsi <- pow(sd.lpsi, -2)                       # Community precision of occupancy probability
#     sd.lpsi ~ dunif(0,2)                               # Community dispersion
#
#     # Hyperpriors for community hyperparameters in detection
#     mu.lp ~ dnorm(0,0.2)                              # Community means of detection probability
#     tau.lp <- pow(sd.lp, -2)                          # Community precision of detection probability
#     sd.lp ~ dunif(0,2)                                # Community dispersion
#
#     mu.betalp1 ~ dnorm(0,0.2)
#     tau.betalp1 <- pow(sd.betalp1, -2)
#     sd.betalp1 ~ dunif(0,2)
#     mu.betalp2 ~ dnorm(0,0.2)
#     tau.betalp2 <- pow(sd.betalp2, -2)
#     sd.betalp2 ~ dunif(0,2)
#     mu.betalp3 ~ dnorm(0,0.2)
#     tau.betalp3 <- pow(sd.betalp3, -2)
#     sd.betalp3 ~ dunif(0,2)
#     mu.betalp4 ~ dnorm(0,0.2)
#     tau.betalp4 <- pow(sd.betalp4, -2)
#     sd.betalp4 ~ dunif(0,2)
#
#     # Ecological model for true occurrence (process model)
#     for(k in 1:nspec){                                  # Loop over species
#       for (i in 1:nsite) {                              # Loop over sites
#         logit(psi[i,k]) <- lpsi[k]
#         z[i,k] ~ dbern(psi[i,k])
#       }
#     }
#
#     # Observation model for replicated detection/nondetection observations
#     for(k in 1:nspec){                                  # Loop over species
#       for (i in 1:nsite){                               # Loop over sites
#         for(j in 1:nrep){                               # Loop over survey
#           logit(p[i,j,k]) <- lp[k] +
#                              betalp1[k] * temp[i,j] + betalp2[k] * pow(temp[i,j], 2) +
#                              betalp3[k] * date[i,j] + betalp4[k] * pow(date[i,j], 2)
#           mu.p[i,j,k] <- z[i,k] * p[i,j,k]
#           y[i,j,k] ~ dbern(mu.p[i,j,k])
#
#         # # NOT WORKING YET
#         # # Goodness of Fit
#         #
#         # #Residual
#         # det.residual[i,j,k] <- y[i.j.k] - mu.p[i,j,k]
#         #
#         # # Pearson residuals.
#         # ynew[i,j,k] ~ dbern(mu.p[i,j,k]) # Create simulated dataset to calculate the Bayesian p-value.
#         #
#         # p.det.res[i,j,k] <- (y[i,j,k] - mu.p[i,j,k])/sqrt((mu.p[i,j,k]+0.001)*(1-mu.p[i,j,k]-0.001))
#         # p.det.resnew[i,j,k] <- (ynew[i,j,k] - mu.p[i,j,k])/sqrt((mu.p[i,j,k]+0.001)*(1-mu.p[i,j,k]-0.001))
#         #
#         # RSS[i,j,k]<- pow(p.det.res[i,j,k],2)
#         # RSSnew[i,j,k]<- pow(p.det.resnew[i,j,k],2)
#
#         }
#       }
#     }
#
#     # # Bayesian P-value
#     # pvalue <- mean(sum(RSSnew[])>sum(RSS[]))
#
#     # Derived quantities
#     for(k in 1:nspec){                                  # Loop over species
#       Nocc.fs[k] <- sum(z[,k])                          # Number of occupied sites
#     }
#     for (i in 1:nsite){                                 # Loop over sites
#       Nsite[i] <- sum(z[i,])                            # Number of occurring species at each site
#     }
# }",fill = TRUE)
# sink()
```


**Model dataset ** will run on the all *small* skink species
```{r data1}
splist <- c("Robust Ctenotus", "Eastern Three Lined Skink", "Pale flecked Garden Skink", "South eastern Slider", "Southern Grass Skink", "Shrubland Morethia Skink", "Southern Water Skink", "White's Skink")
dpSS <- dataprep(filepath="./example_msom.csv", specieslist=splist)

# Bundle and summarize data
str(win.dataSS <-list(y = dpSS$y, nsite = dpSS$nsite, nrep = dpSS$nrep, nspec = dpSS$nspec, temp = dpSS$stdtemp, date = dpSS$stddate))

# Initial values
zstSS <- array(1, dim = c(dpSS$nsite, dpSS$nspec)) # Set all species as occurring
initsSS <- function() {list(z = zstSS, lpsi = rnorm(n = dpSS$nspec), lp = rnorm(n = dpSS$nspec), betalp1 = rnorm(n = dpSS$nspec), betalp2 = rnorm(n = dpSS$nspec), betalp3 = rnorm(n = dpSS$nspec), betalp4 = rnorm(n = dpSS$nspec))}
```

**Model Parameters**
Note: Model convergence was based on Rhat values > 1.1 for parameters: "mu.lpsi", "sd.lpsi", "mu.lp", "sd.lp", "mu.betalp1", "sd.betalp1", "mu.betalp2", "sd.betalp2", "mu.betalp3", "sd.betalp3", "mu.betalp4", "sd.betalp4", "Nsite", "Nocc.fs", "lpsi",  and "lp" in the params1 list. 
```{r parameters}
#Parameters monitored
params1 <- c("mu.lpsi", "sd.lpsi", "mu.lp", "sd.lp", "mu.betalp1", "sd.betalp1", "mu.betalp2", "sd.betalp2", "mu.betalp3", "sd.betalp3", "mu.betalp4", "sd.betalp4", "Nsite", "Nocc.fs", "lpsi", "lp", "z")
params2 <- c("mu.lpsi", "sd.lpsi", "lpsi", "lp", "betalp1", "betalp2", "betalp3", "betalp4", "z", "w")

# MCMC settings
ni1 <- 30000   ;   nt1 <- 10   ;   nb1 <- 10000  ;   nc1 <- 3
ni2 <- 12000   ;   nt2 <- 20   ;   nb2 <- 2000   ;   nc2 <- 3

```

**Run Models for all species**
```{r run1}
outSS.1 <- jags(win.dataSS, initsSS, params1, "MSODM_jags_v1.txt", n.chains = nc1, n.thin = nt1, n.iter = ni1, n.burnin = nb1, parallel=T)
saveRDS(outSS.1, "./jagsoutput/MSOSM_jags_v1_spSS.Rds")
outSS.1m <- jags.basic(win.dataSS, initsSS, params2, "MSODM_jags_v1.txt", n.chains = nc2, n.thin = nt2, n.iter = ni2, n.burnin = nb2, parallel=T)
saveRDS(outSS.1m, "./jagsoutput/MSOSM_jags_v1_spSS_mcmc_samples.Rds")

rm(outSS.1, outSS.1m); gc()

outSS.2 <- jags(win.dataSS, initsSS, params1, "MSODM_jags_v2.txt", n.chains = nc1, n.thin = nt1, n.iter = ni1, n.burnin = nb1, parallel=T)
saveRDS(outSS.2, "./jagsoutput/MSOSM_jags_v2_spSS.Rds")
outSS.2m <- jags.basic(win.dataSS, initsSS, params2, "MSODM_jags_v2.txt", n.chains = nc2, n.thin = nt2, n.iter = ni2, n.burnin = nb2, parallel=T)
saveRDS(outSS.2m, "./jagsoutput/MSOSM_jags_v2_spSS_mcmc_samples.Rds")

rm(outSS.2, outSS.2m); gc()

outSS.3 <- jags(win.dataSS, initsSS, params1, "MSODM_jags_v3.txt", n.chains = nc1, n.thin = nt1, n.iter = ni1, n.burnin = nb1, parallel=T)
saveRDS(outSS.3, "./jagsoutput/MSOSM_jags_v3_spSS.Rds")
outSS.3m <- jags.basic(win.dataSS, initsSS, params2, "MSODM_jags_v3.txt", n.chains = nc2, n.thin = nt2, n.iter = ni2, n.burnin = nb2, parallel=T)
saveRDS(outSS.3m, "./jagsoutput/MSOSM_jags_v3_spSS_mcmc_samples.Rds")

rm(outSS.3, outSS.3m); gc()

outSS.4 <- jags(win.dataSS, initsSS, params1, "MSODM_jags_v4.txt", n.chains = nc1, n.thin = nt1, n.iter = ni1, n.burnin = nb1, parallel=T)
saveRDS(outSS.4, "./jagsoutput/MSOSM_jags_v4_spSS.Rds")
outSS.4m <- jags.basic(win.dataSS, initsSS, params2, "MSODM_jags_v4.txt", n.chains = nc2, n.thin = nt2, n.iter = ni2, n.burnin = nb2, parallel=T)
saveRDS(outSS.4m, "./jagsoutput/MSOSM_jags_v4_spSS_mcmc_samples.Rds")

rm(outSS.4, outSS.4m); gc()
```

**Load models** separately to check convergence
```{r}
# rm(list=ls())
splist <- c("Robust Ctenotus", "Eastern Three Lined Skink", "Pale flecked Garden Skink", "South eastern Slider", "Southern Grass Skink", "Shrubland Morethia Skink", "Southern Water Skink", "White's Skink")
dpSS <- dataprep(filepath="./example_msom.csv", specieslist=splist)

#Load the models and mcmc chains from the jags.basic model
v1 <- readRDS("./jagsoutput/MSOSM_jags_v1_spSS.Rds")
v1mc <- readRDS("./jagsoutput/MSOSM_jags_v1_spSS_mcmc_samples.Rds")

v2 <- readRDS("./jagsoutput/MSOSM_jags_v2_spSS.Rds")
v2mc <- readRDS("./jagsoutput/MSOSM_jags_v2_spSS_mcmc_samples.Rds")

v3 <- readRDS("./jagsoutput/MSOSM_jags_v3_spSS.Rds")
v3mc <- readRDS("./jagsoutput/MSOSM_jags_v3_spSS_mcmc_samples.Rds")

v4 <- readRDS("./jagsoutput/MSOSM_jags_v4_spSS.Rds")
v4mc <- readRDS("./jagsoutput/MSOSM_jags_v4_spSS_mcmc_samples.Rds")

# See model summaries
summary(v1)
summary(v2)
summary(v3)
summary(v4)

# See baseline estimates of species-specific occupancy and detection
occ.det.sum(dpSS, v1)
occ.det.sum(dpSS, v2)
occ.det.sum(dpSS, v3)
occ.det.sum(dpSS, v4)

# Calculate species richness at each site for the models
v1sprich <- extract.nsite(v1)
write.csv(v1sprich, "./species_prediction/v1SSNsite.csv")
v2sprich <- extract.nsite(v2)
write.csv(v2sprich, "./species_prediction/v2SSNsite.csv")
v3sprich <- extract.nsite(v3)
write.csv(v3sprich, "./species_prediction/v3SSNsite.csv")
v4sprich <- extract.nsite(v4)
write.csv(v4sprich, "./species_prediction/v4SSNsite.csv")

# Create a list of estimated true occurrence for species at a site, with X and Y coords for that site for visualisation
spp.predv1 <- spp.site(dpSS, v1)
write.csv(spp.predv1, "./species_prediction/v1SpPred.csv")
spp.predv2 <- spp.site(dpSS, v2)
write.csv(spp.predv2, "./species_prediction/v2SpPred.csv")
spp.predv3 <- spp.site(dpSS, v3)
write.csv(spp.predv3, "./species_prediction/v3SpPred.csv")
spp.predv4 <- spp.site(dpSS, v4)
write.csv(spp.predv4, "./species_prediction/v4SpPred.csv")

plotobs.est(dpSS, v1) # Plot observed number of species against estimated number of species
plotocc.det(dpSS, v1) # Plot occupancy vs detection estimate
plotobs.sites(dpSS, v1) # Plot estimated (Nsite) against observed species richness

plotobs.est(dpSS, v2)
plotocc.det(dpSS, v2)
plotobs.sites(dpSS, v2)

plotobs.est(dpSS, v3)
plotocc.det(dpSS, v3)
plotobs.sites(dpSS, v3)

plotobs.est(dpSS, v4)
plotocc.det(dpSS, v4)
plotobs.sites(dpSS, v4)

# Community distribution of average occupancy and detection probability
plotcomm.dist(v1)
plotcomm.dist(v2)
plotcomm.dist(v3)
plotcomm.dist(v4)

plotcovar.relation(dpSS, v1) # Visualize covariate mean relationships for the average species
plotreg.coef(dpSS, v1, v1mc) # Plot regression coefficients
plotdet.covar(dpSS, v1, v1mc) # Predict detection for temperature and rainfall for each of the observed species

plotcovar.relation(dpSS, v2)
plotreg.coef(dpSS, v2, v2mc)
plotdet.covar(dpSS, v2, v2mc)

plotcovar.relation(dpSS, v3)
plotreg.coef(dpSS, v3, v3mc)
plotdet.covar(dpSS, v3, v3mc)

plotcovar.relation(dpSS, v4)
plotreg.coef(dpSS, v4, v4mc)
plotdet.covar(dpSS, v4, v4mc)
```
